\section{Troubleshooting \& Advanced Usage}
\label{sec:guide_trouble}

\subsection{Common Issues}

\begin{description}
    \item[Error: ``Abaqus command not found''] \hfill \\
    The pipeline cannot find the solver. Open \texttt{data/config.json} in a text editor and set \texttt{"abaqus\_cmd"} to the full path of your batch file, e.g.\ \texttt{C:/SIMULIA/Commands/abq2021.bat}.

    \item[Simulation Hangs / Convergence Failure] \hfill \\
    Inspect the \texttt{.msg} file in the job sub-directory inside \texttt{cm\_directory} or \texttt{rea\_directory}.
    \begin{itemize}
        \item ``Too many increments'': Increase \texttt{maxNumInc} in \texttt{data/config.json}.
        \item ``Time increment too small'': The mesh may be too distorted; increase the mesh-size lower bound in the DOE settings.
    \end{itemize}

    \item[Missing HDF5 / XDMF Files] \hfill \\
    The Abaqus Python ODB extraction failed. Check write permissions in the output directory or available disk space. Re-run the conversion phase only:
    \begin{lstlisting}[language=bash]
python scripts/e1_simulation_run.py cm --conv
    \end{lstlisting}

    \item[Stress Mapping Produces All Zeros] \hfill \\
    The CMA HDF5 path pointed to by \texttt{cm\_hdf5\_path} inside the RSA pipeline does not contain valid data. Re-run \texttt{cm --all} first, or pass \texttt{--cma} to the RSA runner:
    \begin{lstlisting}[language=bash]
python scripts/e1_simulation_run.py rsa --cma --sim
    \end{lstlisting}

    \item[Viewer Shows No Elements] \hfill \\
    The clipping mask may be removing everything. Toggle \textbf{Apply clipping mask} off in the Visualization tab or verify that \texttt{data/e\{n\}\_plane\_settings.json} contains valid plane coordinates (regenerate with \texttt{setup\_geometry.py} if needed).
\end{description}

\subsection{Advanced: Running Individual Phases}

Each runner supports granular control. For example, to regenerate geometry only for Exp2 RSA without re-mapping stresses:
\begin{lstlisting}[language=bash]
python scripts/e2_simulation_run.py rsa --sim
\end{lstlisting}

\subsection{Advanced: Customizing Geometry}

To adjust the specimen dimensions:
\begin{enumerate}
    \item Edit the sample geometry file in \texttt{data/input/exp\{n\}/exp\{n\}\_sample01.py}.
    \item Run the process script to re-fit the polynomial model.
    \item Re-run \texttt{setup\_geometry.py} to confirm that the updated outline is displayed correctly before starting simulations.
    \item Run \texttt{rsa/script.py} (Exp1) or \texttt{rsa2/script.py} (Exp2) standalone in Abaqus CAE to verify the new mesh builds correctly before launching a full batch.
\end{enumerate}