\section{Experiment 1: T-Shape Benchmark}
\label{sec:exp_s1}

\textbf{Package:} \texttt{src/Exp\_Data/s1\_exp/}

This sub-package manages the data for the primary Residual Stress benchmark (T-Shape). It includes not only the dimensional data but also the configuration infrastructure for the entire simulation framework.

\subsection{Dimensional Averaging}
\textbf{Scripts:} \texttt{sample\_dim.py}, \texttt{mean\_dim.py}

To ensure the finite element model represents the physical reality, raw caliper measurements from multiple samples are stored and averaged.
\begin{itemize}
    \item \textbf{Raw Data (\texttt{sample\_dim.py}):} Contains lists of measurements for critical features: \texttt{bottom\_width}, \texttt{wall\_width}, \texttt{total\_height}, etc.
    \item \textbf{Mean Calculation (\texttt{mean\_dim.py}):} 
    The function \texttt{DimOne()} aggregates these lists to compute the statistical mean.
    \begin{equation}
        \mu_{width} = \frac{1}{N} \sum_{i=1}^{N} w_i
    \end{equation}
    It creates a dictionary \texttt{Mean\_dim\_wp} which is imported by the Abaqus geometry scripts (Module II) to construct the parametric T-shape.
\end{itemize}

\section{Configuration Interface (User Frontend)}
\label{sec:config_interface}

\textbf{Scripts:} \texttt{write\_input.py}, \texttt{write\_input\_gui.py}

Since manual editing of JSON files is prone to syntax errors, this module provides a robust frontend for simulation management. It consists of a logic layer for validation and a graphical layer for user interaction.

\subsection{Backend Logic and Validation}
\textbf{Class:} \texttt{AbaqusParameters} (in \texttt{write\_input.py})

This class acts as the gatekeeper for simulation integrity. It manages the lifecycle of the configuration data, ensuring that invalid parameters are caught before the simulation pipeline is triggered.

\begin{itemize}
    \item \textbf{Default Initialization:} 
    If a configuration file is missing, the class automatically generates a complete structure with safe default values (e.g., standard steel properties, conservative time steps), ensuring the system is always in a runnable state.
    
    \item \textbf{Physical Constraints Enforcement:} 
    The \texttt{validate\_parameters()} method implements strict physical checks:
    \begin{itemize}
        \item \textbf{Time Stepping:} Ensures \texttt{initialInc}, \texttt{maxInc}, and \texttt{timePeriod} are strictly positive to prevent solver crashes.
        \item \textbf{Directory Existence:} Verifies if the \texttt{work\_directory} actually exists on the disk, alerting the user immediately if a path is invalid.
        \item \textbf{Post-Processing Metadata:} Checks for required keys in the \texttt{conversion\_params} block (e.g., \texttt{MeshType}, \texttt{Piecenum}), which are critical for the correct parsing of ODB files later in the pipeline.
    \end{itemize}
\end{itemize}

\subsection{Graphical User Interface (GUI)}
\textbf{Class:} \texttt{AbaqusConfigGUI} (in \texttt{write\_input\_gui.py})

Built with \texttt{customtkinter}, this application provides a modern, dark-mode friendly dashboard for controlling the experiment. It abstracts the underlying JSON structure into organized input fields.

\begin{itemize}
    \item \textbf{Real-Time Synchronization:} 
    The interface automatically loads existing configurations on startup and maps them to the visual widgets. Any change in the UI is held in memory until explicitly saved.
    
    \item \textbf{Categorized Editing:} 
    Parameters are grouped logically to aid the user workflow:
    \begin{itemize}
        \item \textbf{Material:} Fine-tune Elastic Modulus ($E$), Poisson's ratio ($\nu$), and Density ($\rho$).
        \item \textbf{DOE Settings:} Define the search space for the parametric study by setting Min/Max ranges for Mesh Size and Specimen Length.
        \item \textbf{Solver Control:} Adjust convergence parameters (increments) without needing to know Abaqus keyword syntax.
    \end{itemize}
    
    \item \textbf{Safety Features:} 
    Includes a "Validate" button that runs the backend checks and displays specific error messages (e.g., "Max increment must be positive") via pop-ups, preventing the saving of broken configurations.
\end{itemize}

\subsection{Global Configuration Storage}
\textbf{File:} \texttt{config.json}

This JSON file serves as the "Single Source of Truth" for the entire framework. All modules—from the Geometry Generator (Part II) to the Result Converter (Part I)—read from this file, guaranteeing consistency.

\begin{itemize}
    \item \textbf{Directories:} Defines absolute paths for \texttt{work\_directory}, \texttt{CM\_directory}, and \texttt{REA\_directory}, ensuring all scripts operate in the correct workspace.
    \item \textbf{Mesh Settings:} Defines the \texttt{mesh\_step} and \texttt{length\_step}, which control the granularity of the sensitivity analysis (e.g., testing mesh sizes from 0.78mm to 0.79mm with 0.05mm steps).
    \item \textbf{Conversion Params:} Stores specific metadata (e.g., \texttt{BeginFrame}, \texttt{EndFrame}) used by the generic converters to slice the simulation time history correctly during data extraction.
\end{itemize}